\startproject project_analysis
\environment env_analysis

\setupbackgrounds[page][background=cover]
\starttext
\setupbackgrounds[header][text][frame=none]
\startstandardmakeup[align=top]
\setuppagenumbering[state=stop]
\startcolor[bordeauxred]
%\dontleavehmode
\blank[0cm]
\startalignment[center]
	\ssd Analysis\par
	\ssd I \& II
\stopalignment
\stopcolor
\blank[10.9cm]
\startcolor[darkblue]
\startalignment[flushright]
\dontleavehmode
	\bTABLE
	\setupTABLE[r][each][frame=off]	
	\setupTABLE[c][1][align=left]
	\setupTABLE[c][2][align=right]
	\bTR \bTD Dozent: \eTD \bTD Prof. Dr. Thomas Bauer \eTD \eTR
	\bTR \bTD Satz: \eTD \bTD Scholz Online (\from[scholzonline]) \eTD \eTR
	\bTR \bTD  \eTD \bTD Frog and Owl (\from[frog-n-owl]) \eTD \eTR
	\bTR \bTD  \eTD \bTD Martin Scholz \eTD \eTR
	\bTR \bTD aktualisiert am: \eTD \bTD \currentdate \eTD \eTR
	\eTABLE
\stopalignment
\stopcolor
\page
\stopstandardmakeup
\startalignment[middle]
This Document is set with \ConTeXt{}, using the MKIV branch\\
Many thanks to Hans Hagen for developing so hard on \ConTeXt{} and \LuaTeX{} to providing such a great Document preparation system.
\stopalignment
\startitemize
\item VCRevision = \VCRevision\ current (maximum) working copy revision number
\item VCRevisionMod = \VCRevisionMod\ as VCRevision = \VCRevision, but with an additional note if the working copy contains modified files
\item VCAuthor = \VCAuthor\ author of the last check-in operation
\item VCDateRaw = \VCDateRAW\ date of last check-in in native format of the VCS software
\item VCDateISO = \VCDateISO\ date of last check-in in ISO format YYYY-MM-DD
\item VCDateTEX = \VCDateTEX\ date of last check-in in TeX format YYYY/MM/DD
\item VCTime = \VCTime\ time of last check-in
\item VCModifiedText = \VCModifiedText\ contains the note shown in macro VCRevisionMod = \VCRevisionMod\ if there were modified files.
This macro can be redefined by the user.
\item VCModified = \VCModified\ 0 if there are no modified files in the working copy directory; 1 or 2 if there are modified files.
In general you don't need this macro.
\stopitemize

These macros can be called wherever appropriate. 

Revision: \VCRevision ; Author: \VCAuthor ; Date: \VCDateISO

\startitemize
\item GITHash = \GITHash\ 40-hexdigit SHA1 commit hash
\item GITAbrHash = \GITAbrHash\ abbreviated commit hash  
\item GITParentHashes = \GITParentHashes\ parent hashes
\item GITAbrParentHashes = \GITAbrParentHashes\ abbreviated parent hashes
\item GITAuthorName = \GITAuthorName\ author name
\item GITAuthorEmail = \GITAuthorEmail\ author email
\item GITAuthorDate = \GITAuthorDate\ author date
\item GITCommitterName = \GITCommitterName\ committer name
\item GITCommitterEmail = \GITCommitterEmail\ committer e-mail
\item GITCommitterDate = \GITCommitterDate\ committer date
\stopitemize

\stoptext
\setupbackgrounds[page][background=]

\setupbackgrounds[header][text][frame=off,bottomframe=on]
\setuppagenumbering[state=start,conversion=romannumerals]
\startfrontmatter
\completecontent
\stopfrontmatter

\startbodymatter
\setuppagenumbering[state=start,conversion=]

\product prd_analysis

\stopbodymatter

\startappendices
\setuppagenumbering[state=start,conversion=]
\completeindex
\completepublications[criterium=all]
\stopappendices
\setupbackgrounds[header][text][frame=none]
\char0
\page
\setupbackgrounds[page][background=cover]

\stopproject
